---
title: "Lab 00 - Hello IDS!"
author: "DYLAN HOBMAN"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Ben", "Dylan", "Jamie", 
           "Adam", "Gandom", "Yara"),
  github_username = c("ben-251", "dylanhobman", "jamieewen", 
                      "adce123", "Gand0m", "yarakanaann"), 
  colour = c("plum", "blue", "blue", 
             "white", "red", "peachpuff"),
  hobby = c("badminton", "football", "football", 
            "skiing", "football", "basketball"),
  favourite_number = c(6, 6, 2, 4, 4, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The data shows each person's username,favourite number and all written in their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

labs() command enables the axis to be labelled.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Add colours to the bar graphs to better distinguish between hobbies, possibly use a pie graph.
